Experiment 1a (Root Questions in Context): Pre-processing

### 2022-11-11 analysis/03_experiment/rscripts/graphs.Rmd
better violin plots

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating)) %>% 
  summarize(CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin.pdf",width=6,height=4)
```

>>>>

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating)) %>% 
  # summarize(CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  # mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```

### 2022-11-11 analysis/03_experiment/rscripts/pre-processing.Rmd
better violin plots

---
title: "Pre-processing Data from Root Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

length(unique(failed_controls$workerid)) # 35
length(unique(failed_controls$workerid))/length(unique(d$workerid))*100 # 5.3%
```

@@

nrow(test) #71980
```

@@

@@

```{r}
agr = test %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

@@

>>>>

---
title: "Experiment 1a (Root Questions in Context): Pre-processing"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

length(unique(failed_controls$workerid)) # 35
length(unique(failed_controls$workerid))/length(unique(d$workerid))*100 # 5.5%
```

@@

nrow(test) #71980

# How many test items?
length(unique(test$tgrep_id)) # 995
```

@@

# Re-Order the paraphrase levels so 'the' is green
agr$paraphrase <- factor(agr$paraphrase, levels=c("a","every","the","other"))

@@

```{r}
agr = test %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the paraphrase levels so 'the' is green
agr$paraphrase <- factor(agr$paraphrase, levels=c("a","every","the","other"))

@@

# Violin plot
```{r}
agr = test %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the paraphrase levels so 'the' is green
agr$paraphrase <- factor(agr$paraphrase, levels=c("a","every","the","other"))

data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-sd(x)
   ymax <- m+sd(x)
   return(c(y=m,ymin=ymin,ymax=ymax))
}

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    # geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin-raw.pdf",width=4,height=2)
```

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
  geom_violin(trim=FALSE,alpha=.4) +  
  geom_dotplot(binaxis='y', stackdir='center',stackratio=1, dotsize=1.2) +
    stat_summary(fun=data_summary, geom="point", shape=18,
                 size=3, color="red") +
    # geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```

@@

# How many remaining?
length(unique(test_norm$tgrep_id)) # 838
